---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```
## My Spending Habits
I tracked my spending for about a week using a Google Form. Each time I made a purchase, I recorded what category it was, how much I spent, and whether it was planned or an impulse buy. This report shows what I found from the data.

```{r load-data}
survey_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vSbvRpsWgdmy787PlcL53MJ-aqF-wNJ_7lBohoySkBWz3DgC_BOfKjJmuwpHlbssB7lxjkfyMAb_JYh/pub?output=csv")

latest_data <- survey_data %>%
  rename(
    category = `What did you mainly spend your money on today?`,
    planned = `Do you think this is an impulse purchase?`
  )
category_summary <- latest_data %>%
  group_by(category) %>%
  summarise(
    count = n(),
    total = sum(`How much money did you spend today? (NZD)`, na.rm = TRUE)
  )
ggplot(latest_data, aes(x = category, fill = planned)) +
  geom_bar() +
  labs(title = "Purchases by category", x = "Category", y = "Count", fill = "Type") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
ggplot(category_summary, aes(x = category, y = total)) +
  geom_bar(stat = "identity") +
  labs(title = "Total spending by category", x = "Category", y = "Total (NZD)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
What I learned
I had `r nrow(latest_data)` purchases in total.

The average amount I spent was $`r mean(latest_data[["How much money did you spend today? (NZD)"]], na.rm = TRUE) %>% round(2)`.

Food & Dinks was my top category with `r category_summary$count[category_summary$category == "Food & Dinks"]` purchases.